---
title: "Project Proposal"
subtitle: "due October 11, 2021 by 11:59 PM "
author: "Mihika Rajvanshi, Bhavika Garg, Michelle Huang"
date: "10/11/2021"
output: pdf_document
---

# Load Packages

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse) 
library(infer)
library(readxl)
library(skimr)
library(dplyr)
``` 

# Load Data
```{r load-data, message = F}
covid1=read_excel("/home/guest/R/the-statistical-power-puffs/data/COVIDiSTRESS_May30_First.xlsx", sheet= 1)
covid2=read_excel("/home/guest/R/the-statistical-power-puffs/data/COVIDiSTRESS_May30_Second.xlsx", sheet= 1)
covid3=read_excel("/home/guest/R/the-statistical-power-puffs/data/COVIDiSTRESS_May 30_Third.xlsx", sheet= 1)
covid4=read_excel("/home/guest/R/the-statistical-power-puffs/data/COVIDiSTRESS_May 30_Fourth.xlsx", sheet= 1)
covid5=read_excel("/home/guest/R/the-statistical-power-puffs/data/COVIDiSTRESS_May 30_Fifth.xlsx", sheet= 1)
```

#Join Data 
```{r join-data, message = FALSE, warning = FALSE}
covidstressdata <-covid1 %>%
  full_join(covid2) %>%
  full_join(covid3) %>%
  full_join(covid4) %>%
  full_join(covid5)
```
Our dataset had to be split in order to upload to github. Here the data is joined. 

# Introduction and Data, including Research Questions

(The introduction should introduce your general research question and your data (where it came from, how it was collected, what are the cases, what are the variables, etc.). Your research questions should be clearly specified. The motivation for your research question should be clear, with citations to relevant literature as appropriate.)

# Glimpse

```{r}
cleancovid <- subset (covidstressdata, select = -c(AD_loss,AD_gain)) #removed because of laTex incompatible symbols in clm 
glimpse(cleancovid)
```


# Data Analysis Plan

(Specify the outcome (response, Y) and predictor (explanatory, X) variables you will use to answer your question, as well as the comparison groups you will use, if applicable. You may include very preliminary exploratory data analysis, including some summary statistics and visualizations, along with some explanation on how they help you learn more about your data. Note the statistical method(s) that you believe will be useful in answering your question(s). 
What results from these specific statistical methods are needed to support your hypothesized answer?)
