---
title: "Mental Health in the COVID-19 Quarantine"
author: "The Statista-Girls: Michelle Huang, Bhavika Garg, Mihika Rajvanshi"
institute: "Duke University"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
# Remove any packages from this list that you're not using
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(infer)
library(readxl)
library(skimr)
library(dplyr)
library(patchwork)
library(broom)
``` 

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(
  fig.retina = 3, 
  dpi = 300, 
  fig.width = 6, 
  fig.asp = 0.618, 
  out.width = "70%"
  )
```

```{r join-data, message = FALSE, warning = FALSE, echo = FALSE, cache = TRUE}
covidstressdata <- read_csv("../data/covidstressdata.csv")
```

```{r clean-data, message = FALSE, warning = FALSE, echo = FALSE, cache = TRUE }
cleancovid <- subset (covidstressdata, select = -c(AD_gain, AD_loss, RecordedDate, Duration..in.seconds., UserLanguage, Dem_edu_mom, Dem_Expat, Dem_state, Dem_riskgroup, AD_check, Trust_countrymeasure)) %>%
filter(Dem_gender %in% c("Male", "Female"), answered_all == "Yes", Dem_isolation %in% c("Isolated", "Life carries on with minor changes", "Life carries on as usual"), Dem_maritalstatus %in% c("Single", "Divorced/widowed", "Married/cohabiting"), Dem_employment %in% c("Not employed", "Retired", "Full time employed", "Student", "Part time employed", "Self-employed"), Dem_dependents %in%c (0, 1, 2, 3, 4, 5, 6, 7, 8, 9), !is.na(PSS10_avg), !is.na(SLON3_avg)) %>%

mutate(Dem_dependentsgrouped = cut(Dem_dependents, breaks = c(-Inf,0,1,2,3,4,Inf)))
```


```{r style-slides, echo = FALSE}
style_xaringan(
  title_slide_background_image = "img/covidpicdark.jpeg"
)
```

class: inverse, middle, center


---

## Data Overview

- COVIDiSTRESS Global Survey (125,000 observations and 152 columns)


- Focused on six explanatory variables: age, gender, level of isolation, marital status, employment status, and number of dependents


- Used the PSS-10 (Perceived Stress Scale) and SLON-3 (Short Self-Report Scale of Social Loneliness) as approximate quantitative measure of mental health 

---

## Research Question 
 - How do age, gender, level of isolation, marital status, number of dependents, and employment affect global mental health outcomes during COVID-19? 
 
 
 - Examined t test and ANOVA tests to determine significance of each explanatory variable
 
 
 - Attempted to create models to predict how the explanatory variables can model predicted PSS-10 and SLON-3 values
 
---

##Demographics Data: Gender

```{r visual-1, warning=FALSE, echo=FALSE, fig.alt = "Distribution of Age in dataset"}
cleancovid %>%
  filter(Dem_gender %in% c("Male", "Female")) %>%
  ggplot(aes(x = Dem_gender, fill = Dem_gender ))+ 
  geom_bar() +
  labs(title= "Gender Distributions", 
       x= "Gender", 
       y= "Individuals", 
       fill = "Gender") + theme(plot.title = element_text(hjust = 0.5))
```

---
##Demographics Data: Age 
```{r visual-2, warning=FALSE, echo=FALSE, message = FALSE, fig.alt = "Distribution of Age in dataset"}
cleancovid %>%
  ggplot(aes(x = Dem_age)) + 
  geom_histogram(fill = "pink") + 
  labs(title= "Age Distributions", 
       x= "Age",
      y= "Individuals") + theme(plot.title = element_text(hjust = 0.5))
```
---
##Demographics Data: Isolation
```{r visual-3, warning=FALSE, echo=FALSE, fig.alt = "Distribution of Isolation Status in our dataset."}
cleancovid %>%
  filter(Dem_isolation %in% c("Isolated", "Life carries on with minor changes", "Life carries on as usual")) %>%
  ggplot(aes(x = Dem_isolation, fill = Dem_isolation)) + 
  geom_bar() + 
  labs(title= "Levels of Isolation", 
       x= "Isolation Level", 
       y= "Individuals", 
       fill = "Level of Isolation") + theme(axis.text.x = element_text(angle=30, hjust =1)) + theme(plot.title = element_text(hjust = 0.5))
```
---
## Distributions of PSS-10 Scales

```{r histogramsslon, echo = FALSE, message = FALSE, warning = FALSE, fig.alt="Histogram showing approximately normal distribtion of PSS10 means."}
cleancovid %>%
  ggplot(aes(x = PSS10_avg)) + 
  geom_histogram(fill = "blue") +
  labs(title = "Distribution of PSS10 Averages", 
       x = "PSS10 Averages", 
       y = "Count")  + theme(plot.title = element_text(hjust = 0.5))
```
---
## Distributions of SLON-3 Scales

```{r histogramspss, echo = FALSE, message = FALSE, warning = FALSE, fig.alt = "Histogram showing normal distribution of SLON3 means"}
cleancovid %>%
  ggplot(aes(x = SLON3_avg)) + 
  geom_histogram(fill = "red") +
  labs(title = "Distribution of SLON Averages", 
       x = "SLON Averages", 
       y = "Count")  + theme(plot.title = element_text(hjust = 0.5))
```

---
## T-Test for Gender (Relationships and Table)
```{r ttestcode, echo = FALSE}
# In this chunk I'm doing a bunch of analysis that I don't want to present 
# in my slides. But I need the resulting data frame for a plot I want to present.
genderPSSttest <- t.test(PSS10_avg~Dem_gender, data= cleancovid, var.equal=FALSE)
genderSLONttest <- t.test(SLON3_avg~Dem_gender, data= cleancovid, var.equal =FALSE)
```

- This table shows all the p-values for t-tests between gender and our PSS-10 and SLON-3 scales. The p value was below 0.05 and 0 was not in the confidence interval. 


```{r ttest-table, echo=FALSE, warning = FALSE, fig.height = 9, fig.alt = "Table of P-values for t-tests between gender and PSS10 and SlON3 showing that the mean PSS10 and SLON3 values are significantly different based on gender."}
ttesttab <- matrix(c(2.23*10^-219, 1.16*10^-135, 
                     0.211, 0.221,
                     0.239, 0.259), 
                    ncol=2, byrow=TRUE)
colnames(ttesttab) <- c('PSS','SLON')
rownames(ttesttab) <- c('P values', 'Confidence Intervals Low', 'Confidence Intervals High')
tttesttab <- as.table(ttesttab)
kable(ttesttab,digits=10,caption="T-Test Results for Gender with PSS and SLON Scales", format = "html")
```

---

## ANOVA Tests: P Values
```{r anova-isolation, echo=FALSE, warning = FALSE}
anovaPSSisolation <- summary(aov(cleancovid$PSS10_avg~cleancovid$Dem_isolation))
anovaSLONisolation <-summary(aov(cleancovid$SLON3_avg~cleancovid$Dem_isolation))
anovaPSSmarital <- summary(aov(cleancovid$PSS10_avg~cleancovid$Dem_maritalstatus))
anovaSLONmarital <-summary(aov(cleancovid$SLON3_avg~cleancovid$Dem_maritalstatus))
anovaPSSemploy <- summary(aov(cleancovid$PSS10_avg~cleancovid$Dem_employment))
anovaSLONemploy <-summary(aov(cleancovid$SLON3_avg~cleancovid$Dem_employment))
anovaPSSdepend <- summary(aov(cleancovid$PSS10_avg~cleancovid$Dem_dependentsgrouped))
anovaSLONdepend <-summary(aov(cleancovid$SLON3_avg~cleancovid$Dem_dependentsgrouped))
```

- This table shows all the p-values for ANVOA between Isolation Status, Marital Status, Employment, Dependents, and our PSS-10 and SLON-3 scales. The p value was below 0.05 in every ANOVA test. This gives us evidence to conduct step down tests. 

```{r anova-ptable, echo=FALSE, warning = FALSE, fig.alt = "Table of P-values for ANOVA tests between explanatory and PSS10 and SlON3 showing that the mean PSS10 and SLON3 values are significantly different based on all explanatory variables"}
anovatab <- matrix(c('<0.0001', '<0.0001',  
                     '<0.0001', '<0.0001',
                     '<0.0001', '<0.0001', 
                     '<0.0001', '<0.0001'), 
                   ncol=2, byrow=TRUE) 
colnames(anovatab) <- c('PSS','SLON')
rownames(anovatab) <- c('Isolation Status', 'Marital Status', 'Employment', 'Dependents')
anovatab <- as.table(anovatab)
knitr::kable(anovatab,digits=10,caption="P Values for ANOVA Results", format = "html")
```

---
##ANOVA Tests: F Values
- This table shows all the F-values for ANVOA between Isolation Status, Marital Status, Employment, Dependents, and our PSS-10 and SLON-3 scales. The p value was above 1 in every ANOVA test. This gives us evidence to conduct step down tests. 

```{r anova-table-Fvalues, echo=FALSE, warning = FALSE,fig.alt = "Table of F-values for ANOVA tests between explanatory and PSS10 and SlON3 showing that the mean PSS10 and SLON3 values are significantly different based on all explanatory variables" }
anovatab_Fvalues <- matrix(c(1547, 1398,
                             22.8, 695, 
                             128, 151, 
                             20.8, 60.5), 
                   ncol=2, byrow=TRUE) 
colnames(anovatab_Fvalues) <- c('PSS','SLON')
rownames(anovatab_Fvalues) <- c('Isolation Status', 'Marital Status', 'Employment', 'Dependents')
anovatab_Fvalues <- as.table(anovatab_Fvalues)
knitr::kable(anovatab_Fvalues,digits=10,caption="F Values for ANOVA Results", format = "html")
```

---
##Step Down Tests: PSS: Isolation and Marital Status
- The significant pairings from PSS-10 Step Down tests for isolation and marital status. All conditions were significant and had p values lower than 0.05.

```{r anovastepdown1, echo = FALSE, warning = FALSE}
anovaPSSisolation_step <- pairwise.t.test(cleancovid$PSS10_avg,cleancovid$Dem_isolation, p.adj = "holm")
sigpairs <- broom::tidy(anovaPSSisolation_step) %>%
  filter(p.value<0.05) %>%
  arrange(group1,group2)
knitr::kable(sigpairs, digits=10,caption="Step-down Test: Isolation", format = "html") 

anovaPSSmarital_step <- pairwise.t.test(cleancovid$PSS10_avg,cleancovid$Dem_maritalstatus, p.adj = "holm")
sigpairs <- broom::tidy(anovaPSSmarital_step) %>%
  filter(p.value<0.05) %>%
  arrange(group1,group2)
knitr::kable(sigpairs, digits=10,caption="Step-down Test: Marital status", format = "html") 
```
---

##Step Down Tests: PSS: Employment
- The significant pairings from PSS-10 Step Down tests for employment. All conditions in employment were significant and had p values lower than 0.05. 

```{r anovastepdown2, echo = FALSE, warning = FALSE}
anovaPSSemploy_step <- pairwise.t.test(cleancovid$PSS10_avg,cleancovid$Dem_employment, p.adj = "holm")
sigpairs <- broom::tidy(anovaPSSemploy_step) %>%
  filter(p.value<0.05) %>%
  arrange(group1,group2)
knitr::kable(sigpairs, digits=10,caption="Step-down Test: Employment", format = "html") 
```
---
##Step Down Tests: PSS: Dependents

- Not all pairings from the dependents are significant. Only pairs that compare 0 dependents to any number of dependents are significant. This shows that having 1,2, 3, 4, 4+ dependents are not significantly different in terms of PSS means. 
```{r anovastepdown3, echo = FALSE, warning = FALSE}
anovaPSSdepend_step <- pairwise.t.test(cleancovid$PSS10_avg,cleancovid$Dem_dependentsgrouped, p.adj = "holm")
sigpairs <- broom::tidy(anovaPSSdepend_step) %>%
  filter(p.value<0.05) %>%
  arrange(group1,group2)
knitr::kable(sigpairs, digits=10,caption="Step-down: Dependents", format = "html") 
```
---

##Step Down Tests: SLON3: Isolation and Marital Status
- The significant pairings from SLON-3 Step Down tests for isolation and marital status. All conditions were significant and had p values lower than 0.05.
```{r SLONstepdown1, echo = FALSE, warning = FALSE}

anovaSLONisolation_step <- pairwise.t.test(cleancovid$SLON3_avg,cleancovid$Dem_isolation, p.adj = "holm")
sigpairs <- broom::tidy(anovaSLONisolation_step) %>%
  filter(p.value<0.05) %>%
  arrange(group1,group2)
knitr::kable(sigpairs, digits=10,caption="Step-down: Isolation", format = "html") 

anovaSLONmarital_step <- pairwise.t.test(cleancovid$SLON3_avg,cleancovid$Dem_maritalstatus, p.adj = "holm")
sigpairs <- broom::tidy(anovaSLONmarital_step) %>%
  filter(p.value<0.05) %>%
  arrange(group1,group2)
knitr::kable(sigpairs, digits=10,caption="Step-down: Marital status", format = "html") 
```
---

##Step Down Tests: SLON3: Employment
- The significant pairings from SLON-3 Step Down tests for employment. All conditions in employment were significant and had p values lower than 0.05. 

```{r SLONstepdown2, echo = FALSE, warning = FALSE, message= FALSE}
anovaSLONemploy_step <- pairwise.t.test(cleancovid$SLON3_avg,cleancovid$Dem_employment, p.adj = "holm")
sigpairs <- broom::tidy(anovaSLONemploy_step) %>%
  filter(p.value<0.05) %>%
  arrange(group1,group2)
knitr::kable(sigpairs, digits=10,caption="Step-down: Employment") 
```
---
##Step Down Tests: SLON3: Dependents
- The significant pairings from SLON-3 Step Down tests for dependents. All conditions in dependents were significant.This means that having any different number of dependents leads to a significant different in SLON-3 values (different than PSS-10).
```{r SLONstepdown3, echo = FALSE, warning = FALSE, message= FALSE}
anovaSLONdepend_step <- pairwise.t.test(cleancovid$SLON3_avg,cleancovid$Dem_dependentsgrouped, p.adj = "holm")
sigpairs <- broom::tidy(anovaSLONdepend_step) %>%
  filter(p.value<0.05) %>%
  arrange(group1,group2)
knitr::kable(sigpairs, digits=10,caption="Step-down: Dependents") 
```

---
## Linear Regression: Age versus PSS10
-We created a linear regression model looking at the impact of age on mean PSS10 and SLON3 values. 

```{r lin-reg-age, echo=FALSE, warning = FALSE, message = FALSE}
covid_PSSage <- linear_reg() %>%
  set_engine("lm") %>%
  fit(PSS10_avg~Dem_age, data = cleancovid)
  covid_PSSage_tidy <- tidy(covid_PSSage, conf.int=TRUE)
  
covid_SLONage <- linear_reg() %>%
  set_engine("lm") %>%
  fit(SLON3_avg~Dem_age, data = cleancovid)
  covid_SLONage_tidy <- tidy(covid_SLONage, conf.int = TRUE)
```

```{r plot-lin-reg-agepss, echo=FALSE, warning = FALSE, message = FALSE}
ggplot(data = cleancovid, 
       aes(x = Dem_age, 
           y = PSS10_avg)) +
  geom_point(alpha=.5) +
  geom_smooth(method = "lm",
              se = FALSE, 
              color = "pink") +
  labs(
    title = "PSS means and Age",
    x = "Age",
    y = "PSS means"
      ) + theme(plot.title = element_text(hjust = 0.5))  
```

---
## Linear Regression: Age versus SLON3

```{r plot-lin-reg-ageslon, echo=FALSE, message= FALSE, warning = FALSE}
ggplot(data = cleancovid, 
       aes(x = Dem_age, 
           y = SLON3_avg)) +
  geom_point(alpha=.5) +
  geom_smooth(method = "lm",
              se = FALSE, 
              color = "blue") +
  labs(
    title = "SLON means and Age",
    x = "Age",
    y = "SLON means"
      ) + theme(plot.title = element_text(hjust = 0.5))
```
---
##Estimates and P-values for age regression model for PSS10 and SLON3

```{r lin-reg-table, echo=FALSE}
lin_reg_table <- matrix(c(-0.014, -0.013,
                          "<0.0001", "<0.0001", 
                          3.145, 3.047,
                          3.183, 3.099), 
                          ncol=2, byrow=TRUE)
colnames(lin_reg_table) <- c('PSS','SLON')
rownames(lin_reg_table) <- c('Estimate', 'P values', 'Confidence Intervals Low', 'Confidence Intervals High')
lin_reg_table <- as.table(lin_reg_table)
knitr::kable(lin_reg_table,digits=10,caption="Linear Regression Results for Age with PSS and SLON Scales") 
```

```{r lin-reg-equations-table, echo=FALSE}
lin_reg_equations_table <- matrix(c('y_expected = 3.164 - 0.014(age)', 
                                    'y_expected = 3.073 - 0.013(age)' 
                                    ),  
                          ncol=2, byrow=TRUE)
colnames(lin_reg_equations_table) <- c('PSS','SLON')
rownames(lin_reg_equations_table) <- c('Equation')
lin_reg_equations_table <- as.table(lin_reg_equations_table)
knitr::kable(lin_reg_equations_table,digits=10,caption="Linear Regression Results for Age with PSS and SLON Scales")
```
---

##Main Effects Model: PSS10
- Next, we created a main effect model incorporating all our explanatory variables for PSS10. The equation is:
<$\hat{y} = \hat{\beta}_0 + \hat{\beta}_1 Male + \hat{\beta}_2 Age + \hat{\beta}_3 Maried/Cohabiting + \hat{\beta}_4 Single +\hat{\beta}_5 Life as Usual + \hat{\beta}_6 Life with Minor Changes + \hat{\beta}_7 Not Employed + \hat{\beta}_8 PartTime+ \hat{\beta}_9 Retired+ \hat{\beta}_a SelfEmployed+ \hat{\beta}_b 1Dependent+ \hat{\beta}_c 2Dependents+ \hat{\beta}_d 3Dependents+ \hat{\beta}_e 4Dependents + \hat{\beta}_e MoreThan4Dependents$>
```{r lin-reg-overall, echo=FALSE}
covid_PSS <- linear_reg() %>%
  set_engine("lm") %>%
  fit(PSS10_avg~Dem_gender + Dem_age + Dem_maritalstatus + Dem_isolation + Dem_employment + Dem_dependentsgrouped, data = cleancovid)
  covid_PSS_tidy <- tidy(covid_PSS, conf.int=TRUE)
``` 

```{r PSS-maineffect-tables, echo = FALSE}
PSS_maineffect_table <- matrix(c(-0.2037, -0.0116, -0.0260, 0.0786, -0.0673, -0.2342, 0.2092, 0.1192, -0.0064, 0.0808, 0.1197, 0.0714, 0.0711, 0.0835, 0.0826, 0.0856), 
                        ncol=1, byrow=TRUE)
colnames(PSS_maineffect_table) <- c('Estimate')
rownames(PSS_maineffect_table) <- c('Dem_gender: Male', 'Dem_age', 'Dem_maritalstatus: Married/cohabiting', 'Dem_maritalstatus: Single', 'Dem_isolation: Life carries on as usual', 'Dem_isolation: Life carries on with minor changes', 'Dem_employment: Not employed', 'Dem_employment: Part time employed', 'Dem_employment: Retired', 'Dem_employment: Self-employed', 'Dem_employment: Student', 'Dem_dependentsgrouped: 1', 'Dem_dependentsgrouped: 2',  'Dem_dependentsgrouped: 3', 'Dem_dependentsgrouped: 4', 'Dem_dependentsgrouped: 4+')
PSS_maineffect_table <- as.table(PSS_maineffect_table)
knitr::kable(PSS_maineffect_table,digits=10,caption="Main Effect Models: Estimates for PSS: Overall Main Effect", format = "html") 
```

---

##Main Effects Model: SLON3
- Next, we created a main effect model incorporating all our explanatory variables for SLON3. 
- The equation is:
<$\hat{y} = \hat{\beta}_0 + \hat{\beta}_1 Male + \hat{\beta}_2 Age + \hat{\beta}_3 Maried/Cohabiting + \hat{\beta}_4 Single +\hat{\beta}_5 Life as Usual + \hat{\beta}_6 Life with Minor Changes + \hat{\beta}_7 Not Employed + \hat{\beta}_8 PartTime+ \hat{\beta}_9 Retired+ \hat{\beta}_a SelfEmployed+ \hat{\beta}_b 1Dependent+ \hat{\beta}_c 2Dependents+ \hat{\beta}_d 3Dependents+ \hat{\beta}_e 4Dependents + \hat{\beta}_e MoreThan4Dependents$>
```{r lin-reg-overallslon, echo=FALSE}
covid_SLON <- linear_reg() %>%
  set_engine("lm") %>%
  fit(SLON3_avg~Dem_gender + Dem_age + Dem_maritalstatus + Dem_isolation + Dem_employment + Dem_dependentsgrouped, data = cleancovid)
  covid_SLON_tidy <- tidy(covid_SLON, conf.int=TRUE)
```

```{r SLON-maineffect-tables, echo = FALSE}
SLON_maineffect_table <- matrix(c(-0.1947, -0.0010, -0.3214, -0.0922, -0.5862, -0.3988, 0.1591, 0.0122, 0.0370, -0.0693, 0.0116, 0.0330, -0.0016, -0.0176, -0.0694, 0.0031), 
                        ncol=1, byrow=TRUE)
colnames(SLON_maineffect_table) <- c('Estimate')
rownames(SLON_maineffect_table) <- c('Dem_gender: Male', 'Dem_age', 'Dem_maritalstatus: Married/cohabiting', 'Dem_maritalstatus: Single', 'Dem_isolation: Life carries on as usual', 'Dem_isolation: Life carries on with minor changes', 'Dem_employment: Not employed', 'Dem_employment: Part time employed', 'Dem_employment: Retired', 'Dem_employment: Self-employed', 'Dem_employment: Student', 'Dem_dependentsgrouped: 1', 'Dem_dependentsgrouped: 2',  'Dem_dependentsgrouped: 3', 'Dem_dependentsgrouped: 4', 'Dem_dependentsgrouped: 4+')
SLON_maineffect_table <- as.table(SLON_maineffect_table)
knitr::kable(SLON_maineffect_table,digits=10,caption="Main Effect Models: Estimates for SLON: Overall Main Effect", format = "html") 
```
---
##Adjusted R squared Values for Main Effects Model: PSS10 and SLON3

```{r adj-R2-values, echo=FALSE, warning = FALSE}
PSS_R2 <- glance(covid_PSS)$adj.r.squared
SLON_R2 <- glance(covid_SLON)$adj.r.squared
```

```{r adj-R2-values-maineffect-table, echo=FALSE}
maineffect_adjustedR2table <- matrix(c(0.1044, 0.1028), 
                        ncol=1, byrow=TRUE)
colnames(maineffect_adjustedR2table) <- c('Adjusted R^2 Value')
rownames(maineffect_adjustedR2table) <- c('PSS', 'SLON')
maineffect_adjustedR2table <- as.table(maineffect_adjustedR2table)
knitr::kable(maineffect_adjustedR2table,digits=10,caption="Main Effect Models: Adjusted R^2 Values for PSS and SLON", format = "html") 
```

---

##Residual Plot for Main Effects Model: PSS10
```{r residualplot-PSSmaineffect, echo=FALSE}
covid_PSS_aug <- augment(covid_PSS$fit)
ggplot(covid_PSS_aug, mapping = aes(x = .fitted, y = .resid)) + 
geom_point(alpha = 0.5)+
geom_hline(yintercept=0, color = "blue")+
labs(title = "Residual Plot of PSS Main Effect Model", 
     x = "Fitted", 
     y = "Residual")  
```
---
##Residual Plot for Main Effects Model: SLON3
```{r residualplot-SLONmaineffect, echo=FALSE}
covid_SLON_aug <- augment(covid_SLON$fit)
ggplot(covid_SLON_aug, mapping = aes(x = .fitted, y = .resid)) + 
geom_point(alpha = 0.5)+
geom_hline(yintercept=0, color = "blue")+
labs(title = "Residual Plot of SLON Main Effect Model", 
     x = "Fitted", 
     y = "Residual")
```
---

##Adjusted R squared values for Interaction Models

-Because we had low r-squared values for our main effect model, we attempted to run several interaction models to see which one fit the data better.

```{r rsquared table, echo = FALSE, warning = FALSE, message = FALSE}
adjustedR2table <- matrix(c(0.1303, 0.1250, 0.1231, 0.1256, 0.1250, 0.1230, 0.1044, 0.1040, 0.1032), 
                        ncol=1, byrow=TRUE)
colnames(adjustedR2table) <- c('Adjusted R^2 Value')
rownames(adjustedR2table) <- c('PSS: Age+Gender', 'PSS: Employment+Isolation', 'PSS: Marital+Isolation', 'PSS: Age+Isolation', 'PSS: Gender+Isolation', 'PSS: Dependents+Isolation', 'SLON: Age+Gender', 'SLON: Employment+Isolation', 'SLON: Marital+Isolation')
adjustedR2table <- as.table(adjustedR2table)
knitr::kable(adjustedR2table,digits=10,caption="Interaction Models: Adjusted R^2 Values for PSS and SLON", format = "html") 
```

---
## Interaction Models: Age and Gender: PSS 
 - Highest R-squared value of the interaction models. 
```{r interaction-models6, echo=FALSE}
#PSS: age and gender
  PSS_age_gender_interaction <- linear_reg() %>%
  set_engine("lm") %>%
  fit(PSS10_avg~Dem_gender + Dem_age + Dem_maritalstatus + Dem_isolation + Dem_employment + Dem_dependentsgrouped + Dem_age*Dem_gender, data = cleancovid)
  PSS_age_gender_interaction_tidy <- tidy(PSS_age_gender_interaction, conf.int=TRUE)
  PSS_age_gender_R2 <- glance(PSS_age_gender_interaction)$adj.r.squared 
```
---
## Interaction Models: Age and Gender: SLON3 
 - Highest R-squared value of the interaction models. 
 
```{r interaction-models7, echo=FALSE}
  SLON_age_gender_interaction <- linear_reg() %>%
  set_engine("lm") %>%
  fit(SLON3_avg~Dem_gender + Dem_age + Dem_maritalstatus + Dem_isolation + Dem_employment + Dem_dependentsgrouped + Dem_age*Dem_gender, data = cleancovid)
  SLON_age_gender_interaction_tidy <- tidy(SLON_age_gender_interaction, conf.int=TRUE)
  SLON_age_gender_R2 <- glance(SLON_age_gender_interaction)$adj.r.squared 
```

```{r PSS-interaction-tables, echo= FALSE}
# PSS_interaction_table <- matrix(c(3.2849, -0.6019, -0.0148, -0.0498, 0.0613, -0.0898, -0.2354, 0.2086, 0.1204, -0.0100, 0.0768, 0.1167, 0.0685, 0.0697, 0.0797, 0.0823, 0.0799, 0.0105),
#   ncol=1, byrow=TRUE)
# colnames(PSS_interaction_table) <- c('Estimate')
# rownames(PSS_interaction_table) <- c('Intercept', 'Dem_gender: Male', 'Dem_age', 'Dem_maritalstatus: Married/cohabiting', 'Dem_maritalstatus: Single', 'Dem_isolation: Life carries on as usual', 'Dem_isolation: Life carries on with minor changes', 'Dem_employment: Not employed', 'Dem_employment: Part time employed', 'Dem_employment: Retired', 'Dem_employment: Self-employed', 'Dem_employment: Student', 'Dem_dependentsgrouped: 1', 'Dem_dependentsgrouped: 2',  'Dem_dependentsgrouped: 3', 'Dem_dependentsgrouped: 4', 'Dem_dependentsgrouped: 4+', 'Dem_gender: Male * Dem_age')
# PSS_interaction_table <- as.table(PSS_interaction_table)
# knitr::kable(PSS_interaction_table,digits=10,caption="Interaction Effect Models: Estimates for PSS: Overall Interaction Effect Between Age and Gender") 
```
---

## Interaction Models:Residuals PSS10

```{r residualplot-PSSagegender, echo=FALSE} 
# PSS_age_gender_interaction_aug <- augment(PSS_age_gender_interaction$fit)
# 
# graph10 <- ggplot(PSS_age_gender_interaction_aug, mapping = aes(x = .fitted, y = .resid)) + 
# geom_point(alpha = 0.5)+
# geom_hline(yintercept=0, color = "blue")+
# labs(title = "Residual Plot of Interaction of PSS in Age and Gender", 
#      x = "Fitted", 
#      y = "Residual") 
```
---
## Interaction Models:Residuals PSS10
```{r residualplot-SLONagegender, echo=FALSE}
# SLON_age_gender_interaction_aug <- augment(SLON_age_gender_interaction$fit)
# 
# graph11 <- ggplot(SLON_age_gender_interaction_aug, mapping = aes(x = .fitted, y = .resid)) + 
# geom_point(alpha = 0.5)+
# geom_hline(yintercept=0, color = "blue")+
# labs(title = "Residual Plot of Interaction of SLON in Age and Gender", 
#      x = "Fitted", 
#      y = "Residual") 
```
